The {\sc VSPEC} code: Spectroscopic phase curves of 3D exoplanet models in the presence of stellar variability

### 2024-06-03 src/tex/ms.tex
Coppied through section 2.0

>>>>

{Stellar Model \label{sec:star}}

The {\sc VSPEC} star model is designed modularly to allow
for both simple and complex behaviors. Currently, it
is represented by a rectangular grid of points on the stellar surface,
each assigned an effective temperature. At any given time, the model computes
the surface coverage fractions of each temperature visible to the observer, accounting for the
spherical geometry, limb darkening, and any occultation by a transiting planet.

The attributes of the \texttt{Star} class describe the bulk properties of the star, including radius,
period, and the effective temperature of quiet photosphere. Herein we refer to this temperature as the
photosphere temperature to differentiate it from the temperature of spots, faculae, or other sources of variability.

\begin{figure}
    \centering
        \includegraphics[width=0.5\textwidth]{figures/surface_map_and_lc.pdf}
    \script{surface_map_and_lc.py}
    \caption{{\bf Top}: The surface map of a star with spots and faculae during a transit.
    The large circles are spots. Faculae display their 3D structure, as the hot wall is more prevalent near the limbs.
    {\bf Bottom}: An example lightcurve of a spotted star.}
    \label{fig:surface_map}
\end{figure}
